Laws for Creating Trust in the Blockchain Age

### 2017-07-26 tex/article.tex
Processed feedback of Quinten and Otto

  \author*[1]{Johan Pouwelse}
  \author[2]{Martijn de Vos}
  \runningauthor{Johan Pouwelse and Martijn de Vos}
  \affil[1]{Department of Software Technology, Delft University of Technology}
  \affil[2]{Department of Software Technology, Delft University of Technology}
  \title{Laws for Creating Trust in the Blockchain Age}
  \abstract{Humanity's notion of trust is shaped by new platforms operating in the emerging sharing economy, acting as intermediate matchmaker for ride sharing, housing facilities or freelance labour, effectively creating an environment where strangers trust each other. While millions of people worldwide rely on online sharing activities, such services are often facilitated by a few predatory companies, managing trust relations. This centralization of responsibility raises questions about ethical and political issues like regulatory compliance, data portability and monopolistic behaviour. Recently, blockchain technology has gathered a significant amount of support and adoption, due to its inherent decentralized and tamper-proof structure.\\We present a blockchain-powered blueprint for a shared and public \emph{programmable economy}. The focus of our architecture is on four essential primitives: digital identities, blockchain-based trust, programmable money and marketplaces. Trust is established using only historical interactions between strangers to estimate trustworthiness. Every component of our proposed technology stack is designed according to the defining principles of the Internet itself: self-governance, autonomy and shared ownership. Real-world viability of each component is demonstrated with a functional prototype or running code. Our vision is that the highlighted technology stack devises trust, new acts, principles and rules beyond what's possible in current economic, legal and political systems.}
  \keywords{Blockchain, Trust, Programmable Economy, Transactions}

@@

Obtaining agreement from numerous parties during several of the stages of a property transactions, detecting errors, and to preserve tamper-proof logging is a significant challenge.
Central keepers of records are often entrusted with this critical coordination task.
Blockchains clearly have potential here, offering transparency, reducing overhead, and especially providing a single-source-of-truth.
Various reports support this opinion.\footcite{deloitteblockchain}

@@

After conducting a small experiment with our prototype, we conclude that the mean fingerprint matching accuracy is 55\% with the highest value of 67\% for thumb fingers.
While modern computerized systems are able to accurately match fingerprints more that 99\% of the time, these systems are often patented, closed-source and expensive\footcite{nistfingerprint}.
We demonstrated the feasibility of an open-source fingerprint recognition framework, requiring minimal resources.
The ability to capture, process and match fingerprints in mere seconds, renders this concept usable in various scenarios like in remote regions with limited Internet connectivity.
This work provides a solution for portable trust and our framework has been specifically designed to serve as a building block for a self-sovereign identity solution.

@@

We propose a novel architecture to create trust.
Each component of our technology portfolio is designed and implemented based on the philosophy of the Internet itself: self-governance and loosely coupled autonomous systems, interacting with each other.
The essential technology to cultivate trust within our decentralized technology platform is TrustChain, a blockchain built around the notion of transacting real-world entities.
Viability of our proposed technology portfolio is demonstrated in the real-world, with running code.
Our aim is to adopt the programmable economy as a mean to decrease organizational barriers, increase trading efficiency and provide more transparency and openness in existing and new economic systems.

While real-world viability of our blueprint has been proven, there is future work to consider.
Some elements should be expanded, like the Internet-of-Money and our self-sovereign identity solution, to unlock their full potential.
Additionally, we are unsure how our proposed technology exactly impacts existing legal, political and economic systems.
For this, we reach out to companies to get insights in the implications of our systems, retrieve feedback on our architectural design and broaden our knowledge in general.

>>>>

  \author*[1]{Johan Pouwelse}
  \author[2]{Martijn de Vos}
  \runningauthor{Johan Pouwelse and Martijn de Vos}
  \affil[1]{Department of Software Technology, Delft University of Technology}
  \affil[2]{Department of Software Technology, Delft University of Technology}
  \title{Laws for Creating Trust in the Blockchain Age}
  \abstract{Humanity's notion of trust is shaped by new platforms operating in the emerging sharing economy, acting as intermediate matchmaker for ride sharing, housing facilities or freelance labour, effectively creating an environment where strangers trust each other. While millions of people worldwide rely on online sharing activities, such services are often facilitated by a few predatory companies, managing trust relations. This centralization of responsibility raises questions about ethical and political issues like regulatory compliance, data portability and monopolistic behaviour. Recently, blockchain technology has gathered a significant amount of support and adoption, due to its inherent decentralized and tamper-proof structure.\\We present a blockchain-powered blueprint for a shared and public \emph{programmable economy}. The focus of our architecture is on four essential primitives: digital identities, blockchain-based trust, programmable money and marketplaces. Trust is established using only historical interactions between strangers to estimate trustworthiness. Every component of our proposed technology stack is designed according to the defining principles of the Internet itself: self-governance, autonomy and shared ownership. Real-world viability of each component is demonstrated with a functional prototype or running code. Our vision is that the highlighted technology stack devises trust, new acts, principles and rules beyond the possibilities in current economic, legal and political systems.}
  \keywords{Blockchain, Trust, Programmable Economy, Transactions}

@@

Obtaining agreement from numerous parties during several of the stages of a property transactions, detecting errors, and to preserve tamper-proof logging is a significant challenge.
Central keepers of records are often entrusted with this critical coordination task.
Blockchains clearly have potential here, offering transparency, reducing overhead, and especially providing a single-source-of-truth.
Various reports support this opinion.\footcite{deloitteblockchain}\,\footcite{coindesklandregistration}

@@

We conducted a small experiment with our prototype to estimate in how accurately fingerprints are matched.
We conclude that the mean fingerprint matching accuracy is 55\% with the highest value of 67\% for thumb fingers.
While modern computerized systems are able to accurately match fingerprints more that 99\% of the time, these systems are often patented, closed-source and expensive\footcite{nistfingerprint}.
We demonstrated the feasibility of an open-source fingerprint recognition framework, requiring minimal resources.
The ability to capture, process and match fingerprints in mere seconds, renders this concept usable in various scenarios like in remote regions with limited Internet connectivity.
This work provides a solution for portable trust and our framework has been specifically designed to serve as a building block for a self-sovereign identity solution.

@@

We propose a novel architecture to create trust.
Each component of our technology portfolio is designed and implemented based on the philosophy of the Internet itself: self-governance and loosely coupled autonomous systems, interacting with each other.
The essential technology to cultivate trust within our decentralized technology platform is TrustChain, a blockchain built around the notion of transacting real-world entities.
Viability of our proposed technology portfolio is demonstrated in the real-world, with running code.
Our aim is to adopt the programmable economy as a means to decrease organizational barriers, increase trading efficiency and provide more transparency and openness in existing and new economic systems.

While real-world viability of our blueprint has been proven, there is future work to consider.
Some elements should be expanded, like the Internet-of-Money and our self-sovereign identity solution, to unlock their full potential.
Additionally, we are unsure how our proposed technology exactly impacts existing legal, political and economic systems.
For this, we are reaching out to companies to get insights in the implications of our systems, retrieve feedback on our architectural design and broaden our knowledge in general.
